---
title: "SocCult data analysis"
author: "Andreas Jeppesen and Helle Sørensen"
date: "5/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
library(readr)
library(stringr)
```

## We write a function to load all the data and do the necessary cleaning:

```{r}

read_stock <- function(filename) {
  # load data
  data <- read.csv(file = filename)
  
  # create empty filename column
  data$filename <- ""
  # put the filenames into this column
  data$filename <- filename
  # remove the whole path so only the actual filename is left
  data$filename <- gsub("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Social and Cultural Dynamics/Exam/Data_all/",
                        "", data$filename)
  
  # with mutate
  # create trial column by extracting the trial number from the filename (the filename col will be used as iteration col)
  data <- data %>% 
    mutate(
      trial = str_extract(filename, regex("l\\d+")), # getting any number of digits after "l"
      trial = as.numeric(gsub("l", "", trial)),      # removing "l" from the values in the trial col
      
      # Prolong the columns that only have a datapoint in the first row
      wealth_slider = data[1,13],
      weight_mean = data[1,14],
      initial_price = data[1,15],
      own_assessment_sd = data[1,16],
      own_assessment_mean = data[1,17],
      weight_sd = data[1,18],
      initial_n_selling = data[1,19],
      initial_n_buying = data[1,20]
    ) %>%
  
  # Rename x and y columns to what they actually are (x cols are ticks, y cols are CP, n_selling, n_buying)
  # I guess the 2nd and 3rd x column are redundant
    rename(
      tick_no = x,
      CP = y,
      n_selling = y.1,
      n_buying = y.2
    ) %>% 
  
  # Create volatility column based on CP column
    mutate(
      volatility = sd(CP)
    ) %>% 
  
  # de-select columns we don't need:
    select(
      -x.1,
      -color,
      -pen.down.,
      -color.1,
      -pen.down..1,
      -x.2,
      -color.2,
      -pen.down..2
    )
  
  # changing columns to the correct format:
  
  data$tick_no <- as.numeric(data$tick_no)
  data$CP <- as.numeric(data$CP)
  data$n_selling <- as.numeric(data$n_selling)
  data$n_buying <- as.numeric(data$n_buying)
  data$wealth_slider <- as.numeric(data$wealth_slider)
  data$weight_mean <- as.numeric(data$weight_mean)
  data$initial_price <- as.numeric(data$initial_price)
  data$own_assessment_sd <- as.numeric(data$own_assessment_sd)
  data$own_assessment_mean <- as.numeric(data$own_assessment_mean)
  data$weight_sd <- as.numeric(data$weight_sd)
  data$initial_n_selling <- as.numeric(data$initial_n_selling)
  data$initial_n_buying <- as.numeric(data$initial_n_buying)
  data$filename <- as.factor(data$filename)
  data$trial <- as.factor(data$trial)
  data$volatility <- as.numeric(data$volatility)
  
  # return data
  return(data)
}



# Create a list with all the data:
list <- list.files(path = "C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Social and Cultural Dynamics/Exam/Data_all" , pattern = "*.csv", all.files = FALSE, full.names = TRUE)






# Let's try out the function:

#testlist <- list[1:4]

#stock_data <- testlist %>% 
#  purrr::map_df(read_stock)

# Looks like it's working. Nice!



# Reading all the data:
stock_data <- list %>% 
  purrr::map_df(read_stock)

# Create a W2 column
stock_data <- stock_data %>% 
  mutate(
    W2 = 1 - weight_mean
  )

```





Test chunk for testing functions for the read_stock function and identifying bad files:

```{r}
df <- read.csv("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Social and Cultural Dynamics/Exam/Data/trial1iteration0.723053789848823.csv")




# Prolonging columns can be done like so:
df <- df %>% 
  mutate(
    wealth_slider = df[1,13],
    weight_mean = df[1,14],
    initial_price = df[1,15]
  )


# Filename column is created like so:
df$filename <- ""
df$filename <- "C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Social and Cultural Dynamics/Exam/Data/trial1iteration0.723053789848823.csv"

# And the path is removed from the name like so:
df$filename <- gsub("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Social and Cultural Dynamics/Exam/Data/", "", df$filename)

df <- df %>% 
  mutate(
    trial = str_extract(df$filename, regex("l\\d+")), # getting any number of digits after l
    iteration = str_extract(df$filename, regex("n\\d+")) #This does not work, so we ust use the filename col as the iteration col
  )


# Trying to de-select some columns:
df <- df %>% 
  select(
    -x.2,
    -color,
    -color.1
  )





# A for loop for identifying files with error in them:
for(i in list) {
  i <- read_stock(i)
}

print(list)





```



Plotting the data in nice ways

```{r}
library(ggplot2)


# A line graph example of a price development

t1w0.05 <- stock_data %>% 
  filter(
    trial == 1 & weight_mean == 0.05
  ) %>% 
  ggplot() +
  geom_line(aes(x = tick_no, y = CP)) +
  theme_minimal() +
  xlab("Tick") +
  ylab("Current Price") +
  ggtitle("Price development at mean weight 0.05, trial 1")

t1w0.05




# Plotting volatility at different weights, trial 1

volplott1 <- stock_data %>% 
  filter(
    trial == 1 & weight_mean > 0 & weight_mean < 0.51
    ) %>% 
  ggplot() +
  geom_point(aes(x = W2, y = volatility)) +
  geom_line(aes(x = W2, y = volatility)) +
  theme_minimal() +
  xlab("Mean W2") +
  ylab("Volatility") +
  ggtitle("Volatilities at varying W2 means in trial 1")

volplott1




# Plotting volatility at different weights [0.01;0.05], trial 8

volplott8 <- stock_data %>% 
  filter(
    trial == 8 & weight_mean > 0 & weight_mean < 0.06
    ) %>% 
  ggplot() +
  geom_point(aes(x = weight_mean, y = volatility)) +
  geom_line(aes(x = weight_mean, y = volatility)) +
  theme_minimal() +
  xlab("Mean Weight") +
  ylab("Volatility") +
  ggtitle("Volatilities at varying mean weights in trial 8")

volplott8

```



Plots of fast changes in price and quick stabilization

```{r}
# Fast rise, trial 2
t2w0.7 <- stock_data %>% 
  filter(
    trial == 2 & weight_mean == 0.7
  ) %>% 
  ggplot() +
  geom_line(aes(x = tick_no, y = CP)) +
  theme_minimal() +
  xlab("Tick") +
  ylab("Current Price") +
  ggtitle("Price development at mean weight 0.7, trial 2")

t2w0.7

# Fast drop, trial 3
t3w0.7 <- stock_data %>% 
  filter(
    trial == 3 & weight_mean == 0.7
  ) %>% 
  ggplot() +
  geom_line(aes(x = tick_no, y = CP)) +
  theme_minimal() +
  xlab("Tick") +
  ylab("Current Price") +
  ggtitle("Price development at mean weight 0.7, trial 3")

t3w0.7


# Plot of t2 and t1 for comparison:
t1and2w0.3 <- stock_data %>% 
  filter(
    trial == 1 & weight_mean == 0.30 |
      trial == 7 & weight_mean == 0.30
  ) %>% 
  ggplot() +
  geom_line(aes(x = tick_no, y = CP, color = trial)) +
  theme_minimal() +
  xlab("Tick") +
  ylab("Current Price") +
  ggtitle("Price development at mean weight 0.3") +
  labs(color = "Trial")

t1and2w0.3

```


Plotting volatility over weights for all trials:

```{r}

# All trials in one plot
volplot <- stock_data %>% 
  filter(
    weight_mean > 0.04 & weight_mean < 0.31
    ) %>% 
  ggplot(aes(x = weight_mean, y = volatility, color = trial)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  xlab("Mean Weight") +
  ylab("Volatility") +
  ggtitle("Volatilities at varying mean weights")

volplot





# A plot for each trial

# Dataframe containing points to highlight
highlight_df <- stock_data %>% 
  filter(
    trial == 1 & weight_mean == 0.10 |
      trial == 2 & weight_mean == 0.14 |
      trial == 3 & weight_mean == 0.10 |
      trial == 4 & weight_mean == 0.12 |
      trial == 5 & weight_mean == 0.13 |
      trial == 6 & weight_mean == 0.12 |
      trial == 7 & weight_mean == 0.11 |
      trial == 8 & weight_mean == 0.13 |
      trial == 9 & weight_mean == 0.10)

volplots <- stock_data %>% 
  filter(
    weight_mean > 0.03 & weight_mean < 0.31
    ) %>% 
  ggplot(aes(x = W2, y = volatility)) +
  geom_point(size = 1.5) +
  geom_line() +
  theme_minimal() +
  xlab("Mean W2") +
  ylab("Volatility") +
  ggtitle("Volatility at varying W2 means") +
  facet_wrap(.~trial, labeller = labeller(trial = c("1" = "Trial 1", "2" = "Trial 2", "3" = "Trial 3", "4" = "Trial 4", "5" = "Trial 5", "6" = "Trial 6", "7" = "Trial 7", "8" = "Trial 8", "9" = "Trial 9"))) +
  geom_point(data = highlight_df, aes(x = W2, y = volatility), color = "red", size = 2.5)

volplots


# Looking at whether all price developments stabilize at roughly the same price (at large weigths)

#stock_data_large_weights <- stock_data %>% filter(weight_mean > 0.2)

#aggregate(stock_data_large_weights$CP, list(stock_data_large_weights$trial), mean)
```


Plot of high volatility at low weight (and low volatility for comparison)

```{r}
# Trial 1, weight 0.5 and 0.95

t1w0.5and0.95 <- stock_data %>% 
  filter(
    trial == 1 & W2 == 0.5 |
      trial == 1 & W2 == 0.95
  ) %>% 
  mutate(
    W2 = as.factor(W2)
  ) %>% 
  ggplot() +
  geom_line(aes(x = tick_no, y = CP, color = W2)) +
  theme_minimal() +
  xlab("Tick") +
  ylab("Current Price") +
  ggtitle("Price development at mean weights 0.5 and 0.95 (Trial 1)")

t1w0.5and0.95

```




